---
title    : Layouts
subtitle : Interactive Docs, UseR 2014
author   : Ramnath Vaidyanathan
mode     : selfcontained # {standalone, draft}
url      : {lib: "../../libraries"}
hitheme  : solarized_light
widgets  : [bootstrap]
editlink : "tutorials/03"
assets:
  js:
    - "http://ajax.googleapis.com/ajax/libs/jqueryui/1.10.3/jquery-ui.min.js"
    - "http://bartaz.github.io/sandbox.js/jquery.highlight.js"
--- .segue .dark .nobackground

<q>A layout is a mustache template that specifies the markup to render a slide</q>

*** =pnotes

Layouts allow a clean separation of content from design, thereby allowing the same markdown document to be rendered using multiple HTML5 frameworks. The best way to understand layouts is to follow a slide through slidify

--- .segue .dark

## Journey of a Slide

---

<iframe src='../01/assets/img/raw_slide.svg' width=800px height=250px>
</iframe> 

--- .centrepre .bigger

## Slide

    --- {class: class1, bg: yellow, id: id1}
    
    ## Slide Title
    
    Slide Contents


--- .centrepre .bigger &callout #slide1a

## Slide

```{r echo = F, comment = NA, cache = F, results = 'hide'}
slide <- '--- {class: class1, bg: yellow, id: id1}

## Slide Title

Slide Contents'
```

    --- {class: class1, bg: yellow, id: id1}
    
    ## Slide Title
    
    Slide Contents

*** .left

Properties

--- .centrepre .bigger &callout #slide1b

## Slide

    --- {class: class1, bg: yellow, id: id1}
    
    ## Slide Title
    
    Slide Contents

*** .left

Title

--- .centrepre .bigger &callout #slide1c

## Slide

    --- {class: class1, bg: yellow, id: id1}
    
    ## Slide Title
    
    Slide Contents
    
*** .left

Content

---

<iframe src='../01/assets/img/parse_slide.svg' width=800px height=250px>
</iframe> 

--- #payload .centrepre

## Payload

```{r echo = F, comment = NA, results = 'markup'}
payload <- slidify:::parse_slide(slide)
payload[1:8]
```

---

<iframe src='../01/assets/img/layout_slide.svg' width=800px height=250px>
</iframe> 



--- .RAW .bigger .centrepre #layout

## Layout

```html
<slide class="{{ slide.class }}" id="{{ slide.id }}" 
    style="background:{{{ slide.bg }}};">
  <hgroup>
    {{{ slide.header}}}
  </hgroup>
  <article>
    {{{ slide.content }}}
  </article>
</slide>
```

---

<iframe src='../01/assets/img/render_slide.svg' width=800px height=250px>
</iframe>

--- .bigger .centrepre #rendered

## Rendered

```{r render, echo = F, comment = NA}
layout = '<slide class="{{ slide.class }}" id="{{ slide.id }}" style="background:{{{ slide.bg }}};">
  <hgroup>
    {{{ slide.header}}}
  </hgroup>
  <article>
    {{{ slide.content }}}
  </article>
</slide>'
rendered = rCharts::render_template(layout, list(slide = payload))
cat(rendered)
```

--- {class: class1, bg: yellow, id: id1}
    
## Slide Title
    
Slide Contents


--- .segue .dark .nobackground

## Custom Layouts

--- .centrepre #carouselslide .carouselslide

## Carousel


```{r typical1, results = 'asis', comment = NA, echo = F}
writeLines(c("\n\n", 
  paste0("\t", readLines('assets/includes/carousel.txt')), 
"\n\n"))
```

--- .centrepre #carouselslideA &callout .carouselslide

## Carousel

```no-highlight
```{r typical2, results = 'asis', comment = NA, echo = F}
writeLines(c("\n\n", 
  paste0(" ", readLines('assets/includes/carousel.txt')), 
"\n\n"))
```
```

*** .left

Properties


--- .centrepre #carouselslideB &callout .carouselslide

## Carousel

```no-highlight
```{r ref.label = 'typical2', results = 'asis', comment = NA, echo = F}
```
```

*** .left

Title

--- .centrepre #carouselslideC &callout .carouselslide

## Carousel

```no-highlight
```{r ref.label = 'typical2', results = 'asis', comment = NA, echo = F}
```
```

*** .left

Blocks

--- .RAW .smaller

<a class='example'>layout</a>

```{r results = 'asis', echo = F}
writeLines(paste('\t', readLines('../01/assets/layouts/carousel.html')))
```

--- &carousel .span12 #mycarouselslide

<a class='example'>view</a>


*** {class: active, img: "../01/assets/img/split.svg"}

Image 1

*** {img: "../01/assets/img/apply.svg"}

Image 2

<style>
#mycarouselslide img {
  width: 800px;
  height: 600px;
}
</style>

--- bg:lightgoldenrodyellow

## Create Carousel

<a class='example'>Your Turn</a>

### Basic 

1. Open the file `demo/layouts/carousel/index.Rmd`.
2. Run `slidify("index.Rmd")`.
3. Open `index.html`.

### Intermediate


1. Add a second slide displaying a carousel of 4 images.
2. Modify the carousel layout.


--- .dark .segue .nobackground

## Notes

---

## Properties

Slide properties are key-value pairs that are passed to the layout. You can specify class, id and bg and style the slide, either by using built in classes, or specifying additional css.

    --- {class: [class1, class2], id: id}

You can also use symbolic css style prefixes for frequently used properties. For instance, a dot indicates class, a hash refers to id and an ampersand identifies a layout.

    --- .class1 .class2 #id


---
    
## Properties

| **Variable**    | **Description**                       |
|-----------------|---------------------------------------|
| `slide.title`   | The title of the slide with no markup |
| `slide.header`  | The title of the slide with markup    |
| `slide.level`   | The title header level (h1 - h6)      |
| `slide.content` | The contents of the slide sans header |
| `slide.html`    | The contents of the slide with header |
| `slide.num`     | The number of the slide               |
| `slide.id`      | The id assigned to the slide          |
| `slide.class`   | The class assigned to the slide       |
| `slide.bg`      | The background assigned to the slide  |
| `slide.myblock`   | The slide block named myblock       |
| `slide.blocks`  | The slide blocks which are not named  |
| `slide.rendered`| The rendered slide                    |

---

## Blocks

Blocks are slides nested within a slide, identified by three stars. Just like a slide, they can contain  properties, title and content. 

There are two types of blocks - named and unnamed. A block can be named by specifying the property `{name: block1}` (or using the symbolic shortcut `{=block1}`). 

A block with the name `block1` can be accessed in a slide layout as `slide.block1`. The title and content of this block can be accessed as `slide.block1.title` and `slide.block1.content`. Unnamed blocks are aggregated into the namespace `slide.blocks`. 

--- .segue .dark .nobackground

## Inheritance

--- .centrepre .RAW &vcenter .bigger

## Adding a Footer

```
<slide class="{{ slide.class }}">
  <hgroup>
    {{{ slide.header }}}
  </hgroup>
  <article>
    {{{ slide.content }}}  
   
      
   
  </article>
</slide>
```

*** =pnotes

Consider the following layout. Suppose, you want some slides in your deck to display a footer with a logo.

--- .centrepre .RAW &vcenter .bigger

## Adding a Footer

```
<slide class="{{ slide.class }}">
  <hgroup>
    {{{ slide.header }}}
  </hgroup>
  <article>
    {{{ slide.content }}}  
   <footer class = 'logo'>
      <img src = 'path/to/logo'></img>
   </footer>
  </article>
</slide>
```

*** =pnotes

One way is to create a new slide layout adding the custom footer after `{{{ slide.content }}}`, saving it to `assets/layouts` and using it as a custom layout.

However, this is not efficient for two reasons. 

- It is not DRY and repeats code unnecessarily. 
- When the default slide layout is modified, you need to manually modify the custom layout to ensure that layouts are in sync. This could happen when you decide to use a different HTML5 slide framework, which has a different markup for slides. This is where layout inheritance comes to play.

Note that while defining your custom slide layout, you are essentially replacing the `{{{ slide.content }}}` placeholder in the slide layout by `{{{ slide.content }}}` + footer. Slidify provides a mechanism, where layouts can inherit from a parent layout, thereby simplifying the template considerably and keeping thing DRY.

--- .centrepre .RAW &vcenter .bigger

## Adding a Footer

    ---
    layout: slide
    ---    
     
     
        {{{ slide.content }}}  
       <footer class = 'logo'>
          <img src = 'path/to/logo'></img>
       </footer>
      
      
      

*** =pnotes

This is the modified layout for this use-case using inheritance. The YAML front matter indicates that this template inherits from slide, which is the default slide layout.

--- bg:lightgoldenrodyellow

<a class="example">Your Turn</a>

## Using Layouts

### Basic 

1. Open the file `demo/layouts/index.Rmd`.
2. Modify the `logo` property to point to a logo of your choice.
3. Run `slidify("index.Rmd")`.
4. Open `index.html`.

### Intermediate

Modify the default slide layout at `demo/layouts/assets/layouts/slide.html` such that 

1. Every slide has a red line after the title.
2. 


--- .segue .dark .nobackground

## Add DeckJS Extension

---

## Introduction

This is a demo in response to the [following question on SO](http://stackoverflow.com/questions/19348763/how-i-can-include-the-use-of-the-extension-deck-automation-js-when-i-create-a-do?utm_source=dlvr.it&utm_medium=twitter)

> How I can include the use of the extension deck.automation.js when I create a document Rmarkdown-slidify-deck.js in RStudio? It is to show a presentation on a screen with statistical content without interaction from anyone, and when finished will start automatically.

---

## Step 1: Initialize Deck

Initialize the slide deck using `author("mydeck")` and modify `index.Rmd` to

```yaml
---
title       : Add DeckJS Extension
author      : Ramnath Vaidyanathan
framework   : deckjs
mode        : selfcontained
---

```

Run `slidify("index.Rmd")` to create a basic deck. Setting `mode: selfcontained` in the YAML front matter will ensure that the `libraries` folder is copied locally.

We will now download the plugin and incorporate it into libraries. If for some reason, you are unable to download it, you can work with a pre-rendered copy in `demos/layouts/deckext`.

---

## Step 2: Download Extension

Download the extension [automatic](http://github.com/rchampourlier/deck.automatic.js) and add it to [libraries/frameworks/deck/extensions](http://github.com/slidify/add-deck-ext/tree/gh-pages/libraries/frameworks/deckjs/extensions). You can do it manually, or run the following R code from your slide directory.

```{r eval = F, tidy = F}
require(downloader)
download(
  'https://github.com/rchampourlier/deck.automatic.js/archive/master.zip', 
  'automatic.zip'
)
unzip('automatic.zip')
slidify:::copy_dir(
  "deck.automatic.js-master/automatic", 
  "libraries/frameworks/deckjs/extensions/automatic"
)
unlink("automatic.zip")
unlink("deck.automatic.js-master")
```

---

## Step 3: Modify Config.yml

Modify `config.yml` in [libraries/frameworks/deckjs/config.yml](http://github.com/slidify/add-deck-ext/tree/gh-pages/libraries/frameworks/deckjs/config.yml) so that `automatic` is added to the list of extensions.

```yaml
deckjs:
  theme: swiss
  transition: horizontal-slide
  extensions: [goto, hash, menu, navigation, scale, status, automatic]
```

---

## Step 4: Add Snippet

Modify [libraries/frameworks/deckjs/partials/snippet.html](http://github.com/slidify/add-deck-ext/tree/gh-pages/libraries/frameworks/deckjs/partials/snippet.html) by replacing the section at the end of `snippet.html` that initializes the deck, to the following. You can configure the settings for `automatic` in this snippet.

```html
<!-- Initialize the deck -->
<script>
$(function() {
  // required only if the automatic extension is enabled.
  $.extend(true, $.deck.defaults, {
  automatic: {
    startRunning: true,    // true or false
    cycle: false,           // true or false
    slideDuration: 1000 // duration in milliseconds
  }})
  $.deck('.slide');
});
</script>
```

--- .RAW

## Step 5: Add Play/Pause (Optional)

If you wish to add play/pause control as described in the documentation for [automatic](http://github.com/rchampourlier/deck.automatic.js), you will need to modify [libraries/frameworks/deckjs/layouts/deck.html](http://github.com/slidify/add-deck-ext/tree/gh-pages/libraries/frameworks/deckjs/layouts/deck.html), by replacing the `<body>` with the following

```
<!-- Begin slides -->
  
{{{ page.content }}}
<div class='deck-automatic-link' title="Play/Pause">Play/Pause</div>
```

--- .RAW

## Step 6: Custom Duration

If you want to add custom slide durations, you will need to modify [libraries/frameworks/deckjs/layouts/slide.html](http://github.com/slidify/add-deck-ext/tree/gh-pages/libraries/frameworks/deckjs/layouts/slide.html) to

```
<section class="slide {{ slide.class }}" id="{{ slide.id }}" data-duration="{{ slide.duration}}">
  {{{ slide.header }}}
  {{{ slide.content }}}
</section>
```

To set the duration, you will need to add the `duration` property on the same line as the slide separator as `YAML`.

```
--- {duration: 5000}
```

---

<iframe src='../../demos/layouts/deckext/index.html'></iframe>


<!-- rmarkdown v1 -->






