---
title    : Frameworks
subtitle : Interactive Docs, UseR 2014
author   : Ramnath Vaidyanathan
mode     : selfcontained # {standalone, draft}
url      : {lib: "../../libraries"}
hitheme  : solarized_light
editlink : "tutorials/02"
assets:
  js:
    - "http://ajax.googleapis.com/ajax/libs/jqueryui/1.10.3/jquery-ui.min.js"
    - "http://bartaz.github.io/sandbox.js/jquery.highlight.js"
--- .segue .dark .nobackground

<q>A framework is a collection of stylesheets, javascripts and layouts that control the style and appearance of a slide deck.</q>

```{r echo = F, cache = F}
include<- function(file, prefix = "\t"){ 
    writeLines(paste0(prefix, readLines(file)))
}
```


--- .centrepre &vcenter

    ---
    title: Frameworks
    framework: revealjs
    mode: selfcontained
    ---
     
    ## Slide 1
     
    Some content
     
    --- 
     
    ## Slide 2
     
    Some content


--- #high1 .centrepre &vcenter

```{r echo = F, results = 'asis', comment = NA}
include('../../demos/frameworks/index.Rmd')
```

---

<iframe src='../../demos/frameworks/index.html' width=90%></iframe>


--- bg:lightgoldenrodyellow

## Using Frameworks

<a class='example'>Example</a>

1. Open `demos/frameworks/index.Rmd`
2. Run `slidify("index.Rmd")` and Open `index.html`

### Intermediate

Change the `framework` property in `index.Rmd` and run `slidify`

1. deckjs
2. shower

--- .segue .dark .nobackground

<q>A theme is a collection of stylesheets that provides different skins for slide decks generated using the framework.</q>

--- .centrepre &vcenter #high-theme

```{r echo = F, results = 'asis', comment = NA}
include('../../demos/frameworks/solarized/index.Rmd')
```

---

<iframe src='../../demos/frameworks/solarized/index.html'></iframe>

--- bg:lightgoldenrodyellow

## Using Themes

<a class='example'>Example</a>

1. Open `demos/frameworks/solarized/index.Rmd`
2. Run `slidify("index.Rmd")` and Open `index.html`

### Intermediate

Different frameworks support different themes and transitions.

__revealjs__

- theme: solarized, moon, sky, simple, serif, night, moon, default, beige
- transition: default, cube, page, concave, zoom, linear, fade, none

__deckjs__

- theme: web-2.0, neon, swiss
- transition: fade, horizontal-slide, vertical-slide

--- .centrepre

## Vertical Slides

```{r echo = F, results = 'asis', comment = NA, cache = F}
include("../../demos/frameworks/vertical/index.Rmd", " \t")
```

---

<iframe src='../../demos/frameworks/vertical/index.html'></iframe>

--- .segue .dark .nobackground

## ImpressJS

--- .centerpre #impress

```{r echo = F, results = 'asis', comment = NA, cache = F}
include("../../demos/frameworks/impressjs/index.Rmd", " \t")
```

<!-- rmarkdown v1 -->











