---
title       : Interactive Documents
subtitle    : Slidify + OpenCPU
author      : Ramnath Vaidyanathan
job         : R Hacker
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : solarized_light      # 
widgets     : [bootstrap, quiz, interactive]          
mode        : selfcontained # {standalone, draft}
ext_widgets : {rCharts: [libraries/nvd3]}
assets: {jshead: "angular.min.js"}
--- &radio

## Interactive Quiz

What is 1 + 4?

1. 1
2. _5_
3. 3
4. 4

*** .hint

This is a hint

*** .explanation

This is an explanation

---

## Interactive Chart

```{r echo = F, results = 'asis', message = F}
require(rCharts)
haireye <- as.data.frame(HairEyeColor)
n1 <- nPlot(Freq ~ Hair, group = 'Eye', type = 'multiBarChart',
    data = subset(haireye, Sex == "Male")
)
n1$show('inline')
```

--- &interactive

## Interactive Console

```{r opts.label = 'interactive', results = 'asis', message = F}
require(googleVis)
M1 <- gvisMotionChart(Fruits, idvar = 'Fruit', timevar = 'Year')
print(M1, tag = 'chart')
```

---

## Interactive App

<div ng-app>
  <div ng-controller='controller1'>
    <input ng-model="n" type="number"></input>
    <select ng-model="col" ng-options="col for col in cols"></select>
    <select ng-model="dist" ng-options="dist for dist in dists"></select>
    <iframe id="outcode" height=300></iframe>
  </div>
  <script>
    function controller1($scope){
      $scope.n = 100
      $scope.dists = ["rnorm", "runif"]
      $scope.dist = $scope.dists[1]
      $scope.cols = ["steelblue", "darkred"]
      $scope.col = $scope.cols[0]     
      $scope.code = function(col, dist, n){
        return "x=" + dist + "(" + n + ");hist(x, col='" + col + "')"
      }
      $scope.$watchCollection("[col, dist, n]", function(){
        runCode2($scope.code($scope.col, $scope.dist, $scope.n), "outcode")
      })
    } 
  </script>
</div>


<!-- rmarkdown v1 -->
