---
title       : How Slidify Works?
subtitle    : Interactive Docs, UseR 2014
author      : Ramnath Vaidyanathan
hitheme     : solarized_light 
mode        : selfcontained # {standalone, draft}
assets:
  js:
    - "http://ajax.googleapis.com/ajax/libs/jqueryui/1.10.3/jquery-ui.min.js"
    - "http://bartaz.github.io/sandbox.js/jquery.highlight.js"
  css: "http://fonts.googleapis.com/css?family=Crimson+Text"
---

```{r setup, cache = F, message = F, eval = T, echo = F}
knitr::knit_hooks$set(document = function(doc){
  gsub("``x", "```", doc)
})
```

--- .segue .dark .nobackground

## Page (Rmd)

--- .centrepre

```{r page0, results = 'asis', comment = NA, echo = F}
writeLines(paste0("\t", readLines('assets/includes/page.txt')))
```

--- &callout #step3a .centrepre


```{r page, results = 'asis', comment = NA, echo = F}
writeLines(paste0("\t", readLines('assets/includes/page.txt')))
```

*** #draggable5 .left

Properties

--- &callout #step3b .centrepre


```{r ref.label='page', results = 'asis', comment = NA, echo = F}
```

*** #draggable6 .left

Section

--- &callout #step3c .centrepre


```{r ref.label='page', results = 'asis', comment = NA, echo = F}
```

*** #draggable7 .left

Separator

--- &callout #step3d .centrepre


```{r ref.label='page', results = 'asis', comment = NA, echo = F}
```

*** #draggable8 .right

Markdown


--- &callout #step3e .centrepre


```{r ref.label='page', results = 'asis', comment = NA, echo = F}
```

*** #draggable9 .right

Code Chunk

---

<iframe src='../01/assets/img/knit.svg' width=800px height=250px>
</iframe> 

--- .centrepre #page1

```{r page1, results = 'asis', comment = NA, echo = F}
writeLines(paste0("\t", readLines('assets/includes/page1-out.txt')))
```

---

<iframe src='../01/assets/img/split_apply_combine.svg' width=800px height=250px>
</iframe> 


---

<iframe src='../01/assets/img/split.svg' width=800px height=250px>
</iframe> 


--- .segue .dark .nobackground

## Slide

--- .centrepre


```{r typical1, results = 'asis', comment = NA, echo = F}
writeLines(c("\n\n", 
  paste0("\t", readLines('assets/includes/typical.txt')), 
"\n\n"))
```


--- {id: step1a, tpl: callout, class: 'centrepre'}

```no-highlight

```{r typical, results = 'asis', comment = NA, echo = F}
writeLines(paste0(" ", readLines('assets/includes/typical.txt')))
```

```

*** .right

Properties

--- .centrepre #step1b &callout

```no-highlight

```{r ref.label = 'typical', results = 'asis', comment = NA, echo = F}
```

```

*** .left

Title

--- .centrepre #step1c &callout

```no-highlight

```{r ref.label = 'typical', results = 'asis', comment = NA, echo = F}
```

```

*** .left

Content

--- .centrepre #step1d &callout

```no-highlight

```{r ref.label = 'typical', results = 'asis', comment = NA, echo = F}
```

```

*** .left

Blocks

---

<iframe src='../01/assets/img/apply.svg' width=800px height=250px>
</iframe> 


---

<iframe src='../01/assets/img/combine.svg' width=800px height=250px>
</iframe> 


--- .segue .dark .nobackground

## Backup Slides

--- .dark .nobackground .segue

## Code Chunks

--- .centrepre &callout #chunk1

    ``x{r example, fig.width = 6, comment = NA}
    x <- 1+1
    rnorm(5)
    ```
    
*** .left #markup build:true

Markup

*** .top #label build:true

Label


*** .top #options build:true

Options

*** .bottom #code1 build:true

Code

--- .centrepre &callout #chunk2



```{r example1, results = 'asis', comment = NA, echo = F}
writeLines(paste0("\t", readLines('assets/includes/example.R')))
```


    
*** .left #markup

Markup

--- .dark .quote .nobackground

<q>The overriding design goal for Markdown’s formatting syntax is to make it as readable as possible. The idea is that a Markdown-formatted document should be publishable as-is, as plain text, without looking like it’s been marked up with tags or formatting instructions.</q>

<!-- rmarkdown v1 -->






